---
title: "Practical machine learning"
author: "Vladimir Emelchenkov"
date: "Sunday, May 24, 2015"
output: html_document
---

1. Project description

The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har. 

The goal of your project is to predict the manner in which people did the exercise. This is the "classe" variable in the training set. 

2. Loading data
```{r}
library(caret)
pmlTesting <- read.csv("pml-testing.csv")
pmlTraining <- read.csv("pml-training.csv")
```

3. Preprocessing data
```{r}
# Removing NAs
pmlTraining[is.na(pmlTraining)] <-0

# Removing near zero variables
nzv <- nearZeroVar(pmlTraining)
pmlTraining <- pmlTraining[, -nzv]

inTrain <- createDataPartition(pmlTraining$classe, p = 0.75, list=F)
training <- pmlTraining[inTrain,]
testing <- pmlTraining[-inTrain,]
```

4. Building CART model
```{r}
modFit <- train(classe ~ ., method="rpart", data=training)
```

5. Estimating out of the sample error
```{r}
predictions <-predict(modFit, newdata = testing)
confusionMatrix(predictions, testing$classe)
```
The accuracy ratio is rather low. The model predicts poorly classes C, D, E. This may be due to ommited variables.

6. Making predictions
```{r}
predict(modFit, newdata = pmlTesting)
```